Semi-supervised author disambiguation of large-scale collections of labeled scientific publications

### 2015-08-05 paper.tex
save

In academic digital libraries, author name disambiguation is the problem of
grouping together publications written by a same person.  Author name
disambiguation is often a difficult problem because an author may use different
spellings, variants or synonyms across her career and/or distinct authors may
share the same name. Most notably, author disambiguation is often even more
troublesome in the case of researchers from non-Western cultures, where
personal names may be traditionally less diverse (leading to homonym issues) or
for which transliteration to latin characters may not be unique (leading to
synonym issues). With the fast growth of the scientific literature, author
disambiguation has become a pressing issue because the accuracy of information
managed at the level of individuals directly affects the relevance search
results (e.g., when querying for all publications written by a given author),
the reliability of bibliometrics and author rankings (e.g., citation counts or other impact
metrics, as studied in \citep{strotmann2012author}) or the relevance of scientific network analysis.

@@

Depending on the type and amount of data available, machine learning approaches
for author disambiguation are usually inventorized into three classes of
algorithms \citep{smalheiser2009author,levin2012citation}.

% levin

>>>>

In academic digital libraries, author name disambiguation is the problem of
grouping together publications written by a same person.  Author name
disambiguation is often a difficult problem because an author may use different
spellings or name variants across her career (synonymy) and/or distinct authors may
share the same name (polysemy). Most notably, author disambiguation is often even more
troublesome in the case of researchers from non-Western cultures, where
personal names may be traditionally less diverse (leading to homonym issues) or
for which transliteration to latin characters may not be unique (leading to
synonym issues). With the fast growth of the scientific literature, author
disambiguation has become a pressing issue because the accuracy of information
managed at the level of individuals directly affects the relevance search
results (e.g., when querying for all publications written by a given author),
the reliability of bibliometrics and author rankings (e.g., citation counts or other impact
metrics, as studied in \citep{strotmann2012author}) or the relevance of scientific network analysis.

@@

As reviewed in
\citep{smalheiser2009author,ferreira2012brief,levin2012citation}, author
disambiguation algorithms are usually composed of two components: (i) a
similarity function determining whether two publications have been written by a
same author and (ii) a clustering algorithm producing clusters of publications
assumed to be written by a same author. Approaches can be inventorized along
several axes, depending on the type and amount of data available, the way the
similarity function is learned or defined, or the clustering procedure used to
group publications. Methods relying on supervised learning usually make use of
hand-labeled pairs of publications identified as being either from the same or
from different authors for learning automatically a similarity function between
publications \citep{han2004two,huang2006efficient,
culotta2007author,treeratpituk2009disambiguating,tran2014author}. Because
training data is often not easily available, unsupervised approaches propose
instead to use domain-specific similarity functions designed for author
disambiguation
\citep{malin2005unsupervised,mcrae2006also,song2007efficient,kang2009co,fan2011graph,schulz2014exploiting}.
These later approaches have the advantage of requiring no hand-labeled data, but
often do not perform as well as the supervised approaches. To reconcile
both worlds, semi-supervised
